---
title: Barplots in the style of Tufte
author: Jason Winget
date: '2019-01-19'
slug: barplots-in-the-style-of-tufte
categories:
  - visualization
tags:
  - Tufte
  - ggplot2
image:
  caption: ''
  focal_point: ''
---

```{r setup, include=FALSE}
# Turn off message spam
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

Lately I've been referencing the classic Tufte book [The Visual Display of Quantitative Information](https://www.edwardtufte.com/tufte/books_vdqi). I don't agree with *everything* tufte has to say, but some of his advice is fantastic.

People who consume my results like bar charts, likely because they're familiar from Excel. I've been working on some ggplot2 settings that generate beautiful barplots.

Here it is:

```{r, echo=T}
library(ggplot2)
library(viridisLite)
library(dplyr)

iris %>%
  group_by(Species) %>%
  summarize(mean.Sepal.Length = mean(Sepal.Length)) %>%
  ggplot(aes(x=Species, y=mean.Sepal.Length, fill=Species)) + geom_col() + 
  theme(panel.background = element_rect(fill = NA),
  panel.ontop = TRUE
) + scale_x_discrete(breaks = NULL) + scale_fill_viridis_d()
```

By unsetting the `panel.background` and adding the `panel.ontop` arguments in the `theme`, you get a very clean chart with white lines indicating the bar heights.

I also only recently learned about the `geom_col` geom in ggplot2 which is like `geom_bar(stat="identity")` but nicer looking :)
