---
title: How to write a data frame to excel without row names in R?
author: Jason Winget
date: '2019-01-24'
slug: how-to-write-a-data-frame-to-excel-without-row-names
categories:
  - I/O
tags:
  - tidy data
  - excel
image:
  caption: ''
  focal_point: ''
---

Got a question today about how to write a data frame to Excel without rownames. Seasoned R vets probably don't even blink at this, but it's the type of thing that I think a lot of new users struggle to overcome.

Anyhow, here are my quick and simple solutions:

The easiest is to write this to a CSV file, which will open in excel. You can use the following code to do this:

```{r, echo=T, eval=F}
# Install/load the readr package
if(!require(readr)){
    install.packages("readr")
    library(readr)
}

# Write out the file
write_csv(my.data.frame, “mytable.csv”)
```

Once again the `tidyverse` comes to the rescue. `write_csv` from the readr package never writes row names to the output file!

Alternatively you could write directly to an excel document using `XLConnect`. This code would look more like the following:

```{r, echo=T, eval=F}
# Install/load the XLConnect package
if(!require(XLConnect)){
    install.packages("XLConnect ")
    library(XLConnect)
}

# Create an output workbook
wb <- loadWorkbook(“myfile.xlsx”, create=TRUE)

# Create a sheet named results in the new workbook
createSheet(wb, ‘results’)

# Write your table to the sheet
writeWorksheet(wb, my.data.frame, ‘results’)

# Save the file
saveWorkbook(wb)
```

There you have it, pretty easy once you know the tools. Keep being awesome!
